Brain Tumor Detection using Machine Learning Models

### 2021-08-04 paper.tex
conclusion

	CT (Computed Tomography), MRI (Magnetic Resonance Imaging), PET (Positron
	Emission Tomography) etc. generates a large amount of image information.
	With the improved technology, not only does the size and resolution of the
	images grow but also the number of dimensions increases. In the future, we
	would like to have algorithms which can automatically detect diseases,
	lesions and tumors, and highlight their locations in the large pile of
	images.

@@

>>>>

	CT (Computed Tomography), MRI (Magnetic Resonance Imaging), PET (Positron
	Emission Tomography) etc. generates a large amount of image information.
	With the improved technology, not only does the size and resolution of the
	images grow but also the number of dimensions increases.

@@

	From this experiment/project we can clearly conclude that the ResNet 50
	outperforms other machine learning models.

	In the future, I would like to have algorithms which can automatically
	detect diseases, lesions and tumors, and highlight their locations in the
	large pile of images.

	I would also like to train using better machine learning models like GAN.
	A generative adversarial network is a class of machine learning frameworks
	designed by Ian Goodfellow and his colleagues in 2014. Two neural networks
	contest with each other in a game. Given a training set, this technique learns
	to generate new data with the same statistics as the training set.

	I also plan on improving and expanding the dataset, which will greatly
	increase our experimental results.
